---
title: "Compiled Code"
author: "Darwin Khay"
date: "11/23/2020"
output:
  pdf_document: default
  html_document: default
---

---
title: "Final Project Data Wrangling"
author: "Darwin Khay"
date: "9/29/2020"
output: html_document
---
# 1. Data Wrangling

# Importing the dataset

```{r}

asmr_data <- read.csv("C:\\Users\\khayd\\Documents\\FALL 2020 Files\\STAT 1601\\Datasets\\ASMR_data.csv")
```

```{r}
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(ggwordcloud)

```

# Subsetting the data to include relevant variables
 
```{r}
#

asmr_data1 <- asmr_data%>%
  select(BDI.group, BDI_TOTAL, BAI_TOTAL,Ill_Elab, V_howmanyvideos, V_Time_Evening, V_Time_BeforeSleep, V_Time_SpareTime, D_Do_you_Experience_tingles,FlowWatching,FlowFeeling,FlowNoEffort,FlowInControl,FlowNotWorried,BeforeMood,During,After,X30mins,hour,X3hour,Day,Daily,EffectSleep,RelieveNegativeMood,EnjoyASMRvideos,EnjoyContentofASMRvideos,WatchToRelax,DealWithAnxiety,DealWithStress,HelpMeSleep,Depression)


```


# Renaming some column names

```{r}

asmr_data2<-asmr_data1%>%
  rename(BDI_group = BDI.group,Illness_Type = Ill_Elab, Num_ASMRVideos = V_howmanyvideos, Watch_EveningTime = V_Time_Evening, Watch_BeforeSleep = V_Time_BeforeSleep, Watch_SpareTime = V_Time_SpareTime, Experienced_Tingles = D_Do_you_Experience_tingles, Mood_Before_watch = BeforeMood, Mood_During_Watch = During, Mood_After_watch = After, MoodAfter_30mins_watch = X30mins, MoodAfter_1hour_watch = hour, MoodAfter_3hours_watch = X3hour, MoodAfter_1Day_watch = Day, Mood_Daily = Daily, EnjoyContentofASMRvideos_notingles = EnjoyContentofASMRvideos, WatchToDealWithDepression = Depression, FlowFocusWatching = FlowWatching)

glimpse(asmr_data2)
```


# Changing some columns into character vectors and changing values

```{r}


asmr_data3 <- asmr_data2%>%
  mutate(BDI_group = as.character(BDI_group))%>%
  mutate(BDI_group = ifelse(BDI_group == "1", "Little to no depression", ifelse(BDI_group == "2", "Mild depression", "Moderate or severe depression")))%>%
  mutate(Illness_Type = ifelse(Illness_Type == "0", NA, Illness_Type))%>%
  mutate(Watch_EveningTime = as.character(Watch_EveningTime), Watch_BeforeSleep = as.character(Watch_BeforeSleep), Watch_SpareTime = as.character(Watch_SpareTime))%>%
  mutate(Watch_EveningTime = ifelse(Watch_EveningTime == "0", "No", "Yes"), Watch_BeforeSleep = ifelse(Watch_BeforeSleep == "0", "No", "Yes"), Watch_SpareTime = ifelse(Watch_SpareTime == "0", "No", "Yes"))%>%
  mutate(Experienced_Tingles = as.character(Experienced_Tingles))%>%
  mutate(Experienced_Tingles = ifelse(Experienced_Tingles == "1", "Yes", "No"))%>%
  mutate(EffectSleep = as.character(EffectSleep))%>%
  mutate(EffectSleep = ifelse(EffectSleep == "1" | EffectSleep == "3", "Yes", "No"))

glimpse(asmr_data3)

```

# Summary measures of key numeric variables

```{r}


BDI_mean_table<-asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(BDI_mean_byBDIgroup = mean(BDI_TOTAL, na.rm=T), BAI_mean_byBDIgroup = mean(BAI_TOTAL, na.rm=T))
BDI_mean_table

BDI_standarddev_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(BDI_sd_byBDIgroup = sd(BDI_TOTAL, na.rm=T), BAI_sd_byBDIgroup = sd(BAI_TOTAL, na.rm=T))
BDI_standarddev_table



NumVids_mean_table<-asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(NumVids_mean_byBDIgroup = mean(Num_ASMRVideos, na.rm=T))
NumVids_mean_table

NumVids_sd_table<-asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(NumVids_sd_byBDIgroup = sd(Num_ASMRVideos, na.rm=T))
NumVids_sd_table



MoodBeforeWatch_mean_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodBeforeWatch_mean_byBDIgroup = mean(Mood_Before_watch, na.rm=T))
MoodBeforeWatch_mean_table

MoodBeforeWatch_sd_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodBeforeWatch_sd_byBDIgroup = sd(Mood_Before_watch, na.rm=T))
MoodBeforeWatch_sd_table



MoodAfterWatch_mean_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodAfterWatch_mean_byBDIgroup = mean(Mood_After_watch, na.rm=T))
MoodAfterWatch_mean_table

MoodAfterWatch_sd_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodAfterWatch_sd_byBDIgroup = sd(Mood_Before_watch, na.rm=T))
MoodAfterWatch_sd_table



MoodAfter30minsWatch_mean_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodAfter30minWatch_mean_byBDIgroup = mean(MoodAfter_30mins_watch, na.rm=T))
MoodAfter30minsWatch_mean_table


MoodAfter30minsWatch_sd_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodAfter30minWatch_sd_byBDIgroup = sd(MoodAfter_30mins_watch, na.rm=T))
MoodAfter30minsWatch_sd_table



MoodAfter1hourWatch_mean_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodAfter1hourWatch_mean_byBDIgroup = mean(MoodAfter_1hour_watch, na.rm=T))
MoodAfter1hourWatch_mean_table

MoodAfter1hourWatch_sd_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodAfter1hourWatch_sd_byBDIgroup = sd(MoodAfter_1hour_watch, na.rm=T))
MoodAfter1hourWatch_sd_table



MoodAfter3hoursWatch_mean_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodAfter3hoursWatch_mean_byBDIgroup = mean(MoodAfter_3hours_watch, na.rm=T))
MoodAfter3hoursWatch_mean_table

MoodAfter3hoursWatch_sd_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodAfter3hoursWatch_sd_byBDIgroup = sd(MoodAfter_3hours_watch, na.rm=T))
MoodAfter3hoursWatch_sd_table


MoodAfter1DayWatch_mean_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodAfter1DayWatch_mean_byBDIgroup = mean(MoodAfter_1Day_watch, na.rm=T))
MoodAfter1DayWatch_mean_table

MoodAfter1DayWatch_sd_table <- asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodAfter1DayWatch_sd_byBDIgroup = sd(MoodAfter_1Day_watch, na.rm=T))
MoodAfter1DayWatch_sd_table



MoodDaily_mean_table<-asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodDaily_mean_byBDIgroup = mean(Mood_Daily, na.rm=T))
MoodDaily_mean_table

MoodDaily_sd_table<-asmr_data3%>%
  group_by(BDI_group)%>%
  summarize(MoodDaily_sd_byBDIgroup = sd(Mood_Daily, na.rm=T))
MoodDaily_sd_table



```


# Summary measures of key categorical variables

```{r}


illness_type_table<-asmr_data3%>%
  select(Illness_Type)%>%
  table()

illness_type_table2<-illness_type_table%>%
  data.frame(illness_type_table)%>%
  select(1,Freq)%>%
  rename(Illness_Type = 1)
illness_type_table3<-illness_type_table2[order(-illness_type_table2$Freq),]
head(illness_type_table3)

twoway_bdigroup_eveningtime <- asmr_data3%>%
  select(BDI_group, Watch_EveningTime)%>%
  table()
twoway_bdigroup_eveningtime


twoway_bdigroup_beforesleep <- asmr_data3%>%
  select(BDI_group, Watch_BeforeSleep)%>%
  table()
twoway_bdigroup_beforesleep


twoway_bdigroup_sparetime <- asmr_data3%>%
  select(BDI_group, Watch_SpareTime)%>%
  table()
twoway_bdigroup_sparetime

experiencedtingles_frequency <- asmr_data3%>%
  select(Experienced_Tingles)%>%
  table()
experiencedtingles_frequency


twoway_bdigroup_flowfocuswatching<-asmr_data3%>%
  select(BDI_group, FlowFocusWatching)%>%
  table()
twoway_bdigroup_flowfocuswatching


twoway_bdigroup_flowfeeling<-asmr_data3%>%
  select(BDI_group, FlowFeeling)%>%
  table()
twoway_bdigroup_flowfeeling

twoway_bdigroup_flownoeffort<-asmr_data3%>%
  select(BDI_group, FlowNoEffort)%>%
  table()
twoway_bdigroup_flownoeffort


twoway_bdigroup_flowincontrol<-asmr_data3%>%
  select(BDI_group, FlowInControl)%>%
  table()
twoway_bdigroup_flowincontrol


twoway_bdigroup_flownotworried<-asmr_data3%>%
  select(BDI_group, FlowNotWorried)%>%
  table()
twoway_bdigroup_flownotworried

twoway_bdigroup_effectsleep <- asmr_data3%>%
  select(BDI_group, EffectSleep)%>%
  table()
twoway_bdigroup_effectsleep

twoway_bdigroup_relievenegativemood <- asmr_data3%>%
  select(BDI_group, RelieveNegativeMood)%>%
  table()
twoway_bdigroup_relievenegativemood


twoway_bdigroup_enjoyasmrvids <- asmr_data3%>%
  select(BDI_group, EnjoyASMRvideos)%>%
  table()
twoway_bdigroup_enjoyasmrvids

twoway_bdigroup_enjoycontentasmrvids_notingles <- asmr_data3%>%
  select(BDI_group, EnjoyContentofASMRvideos_notingles)%>%
  table()
twoway_bdigroup_enjoycontentasmrvids_notingles

twoway_bdigroup_watchtorelax <- asmr_data3%>%
  select(BDI_group, WatchToRelax)%>%
  table()
twoway_bdigroup_watchtorelax

twoway_bdigroup_dealwithanxiety <- asmr_data3%>%
  select(BDI_group, DealWithAnxiety)%>%
  table()
twoway_bdigroup_dealwithanxiety

twoway_bdigroup_dealwithstress <- asmr_data3%>%
  select(BDI_group, DealWithStress)%>%
  table()
twoway_bdigroup_dealwithstress

twoway_bdigroup_helpmesleep <- asmr_data3%>%
  select(BDI_group, HelpMeSleep)%>%
  table()
twoway_bdigroup_helpmesleep

twoway_bdigroup_dealwithdepression <- asmr_data3%>%
  select(BDI_group, WatchToDealWithDepression)%>%
  table()
twoway_bdigroup_dealwithdepression


```


# 2. Data Visualization

# Stacked bar graphs

```{r}

asmr3 <-asmr_data3%>%
  mutate(FlowNotWorried = 
          ifelse(FlowNotWorried == 1, "(1)Feel extremely worried", 
          ifelse(FlowNotWorried == 2, "(2)Feel moderately worried",
          ifelse(FlowNotWorried == 3, "(3)Feel slightly worried",
          ifelse(FlowNotWorried == 4, "(4)Feel almost no worry", 
          ifelse(FlowNotWorried == 5,"(5)Feel no worry", NA))))), 
         FlowInControl = 
          ifelse(FlowInControl == 1, "(1)No control of feelings",
          ifelse(FlowInControl == 2, "(2)Little control of feelings",
          ifelse(FlowInControl == 3, "(3)Moderate control of feelings",
          ifelse(FlowInControl == 4, "(4)Better control of feelings",
          ifelse(FlowInControl ==5,"(5)Full control of feelings", NA))))))%>%
  filter(!is.na(FlowNotWorried), !is.na(FlowInControl))

ggplot(asmr3, aes(x=BDI_group, fill=FlowNotWorried))+
  geom_bar(position = "fill")+
  theme(axis.text.x = element_text(angle = 65, vjust = 0.5),plot.title = element_text(hjust = 0.5), axis.title.x = element_text(vjust = -1))+
  labs(x = "BDI Group ", title = "Worrisomeness of Participants")


ggplot(asmr3, aes(x=BDI_group, fill=FlowInControl))+
  geom_bar(position = "fill")+
  theme(axis.text.x = element_text(angle = 65, vjust = 0.5),plot.title = element_text(hjust = 0.5), axis.title.x = element_text(vjust = -1))+
  labs(x = "BDI Group", title = "Level of control of participants")
```

# Histograms of The Mood of Participants

```{r}

ggplot(asmr_data3, aes(x=Mood_Before_watch))+
  geom_histogram(bins = sqrt(nrow(asmr_data3)), fill="lightpink", color="white")+
  labs(y = "Mood (0-100)", title = "Histogram for Mood Before Watching ASMR videos", x = "Before Mood")+
  theme(plot.title = element_text(hjust = 0.5))

ggplot(asmr_data3, aes(x=Mood_During_Watch))+
  geom_histogram(bins = sqrt(nrow(asmr_data3)), fill="lightpink", color="white")+
  labs(y = "Mood (0-100)", title = "Histogram for Mood While Watching ASMR videos", x = "During Mood")+
  theme(plot.title = element_text(hjust = 0.5))


ggplot(asmr_data3, aes(x=Mood_After_watch))+
  geom_histogram(bins = sqrt(nrow(asmr_data3)), fill="lightpink", color="white")+
  labs(y = "Mood (0-100)", title = "Histogram for Mood After Watching ASMR videos", x = "After Mood")+
  theme(plot.title = element_text(hjust = 0.5))



ggplot(asmr_data3, aes(x=Mood_Daily))+
  geom_histogram(bins = sqrt(nrow(asmr_data3)), fill="lightpink", color="white")+
  labs(y = "Mood (0-100)", title = "Histogram for General Mood", x = "General Mood")+
  theme(plot.title = element_text(hjust = 0.5))
```

# Side-by-side boxplots of Mood of Participants grouped by BDI_group 

```{r}
ggplot(asmr_data3, aes(x = BDI_group,y=Mood_Before_watch))+
  geom_boxplot(fill="aquamarine")+
  labs(y = "Mood (0-100)", title = "Boxplots for Mood Before Watching ASMR videos", x = "BDI group")+
  theme(plot.title = element_text(hjust = 0.5))

ggplot(asmr_data3, aes(x = BDI_group,y=Mood_During_Watch))+
  geom_boxplot(fill="aquamarine")+
  labs(y = "Mood (0-100)", title = "Boxplots for Mood While Watching ASMR videos", x = "BDI group")+
  theme(plot.title = element_text(hjust = 0.5))


ggplot(asmr_data3, aes(x = BDI_group,y=Mood_After_watch))+
  geom_boxplot(fill="aquamarine")+
  labs(y = "Mood (0-100)", title = "Boxplots for Mood After Watching ASMR videos", x = "BDI group")+
  theme(plot.title = element_text(hjust = 0.5))

ggplot(asmr_data3, aes(x = BDI_group,y=Mood_Daily))+
  geom_boxplot(fill="aquamarine")+
  labs(y = "Mood (0-100)", title = "Boxplots for General Mood", x = "BDI group")+
  theme(plot.title = element_text(hjust = 0.5))


```


# Scatterplots of BDI_TOTAL score and Mood of Participants

```{r}
ggplot(asmr_data3, aes(x = BDI_TOTAL, y = Mood_Before_watch))+
  geom_point()+
  geom_smooth(method = "lm")+
  labs(y = "Mood (0-100)", title = "Scatterplot for Mood Before Watching ASMR videos", x = "BDI Total Score")+
  theme(plot.title = element_text(hjust = 0.5))




ggplot(asmr_data3, aes(x = BDI_TOTAL, y = Mood_During_Watch))+
  geom_point()+
  geom_smooth(method = "lm")+
  labs(y = "Mood (0-100)", title = "Scatterplot for Mood While Watching ASMR videos", x = "BDI Total Score")+
  theme(plot.title = element_text(hjust = 0.5))



ggplot(asmr_data3, aes(x = BDI_TOTAL, y = Mood_After_watch))+
  geom_point()+
  geom_smooth(method = "lm")+
  labs(y = "Mood (0-100)", title = "Scatterplot for Mood After Watching ASMR videos", x = "BDI Total Score")+
  theme(plot.title = element_text(hjust = 0.5))




ggplot(asmr_data3, aes(x = BDI_TOTAL, y = Mood_Daily))+
  geom_point()+
  geom_smooth(method = "lm")+
  labs(y = "Mood (0-100)", title = "Scatterplot for General Mood of Participants", x = "BDI Total Score")+
  theme(plot.title = element_text(hjust = 0.5))


```



# Side-by-side boxplots of three key categorical variables

```{r}

asmr3 <-asmr_data3%>%
  mutate(RelieveNegativeMood = 
        ifelse(RelieveNegativeMood==1, "(1)Does not watch to relieve negative mood",
        ifelse(RelieveNegativeMood==2, "(2)Watch to relieve negative mood minimally",
        ifelse(RelieveNegativeMood==3, "(3)Watch to somewhat relieve negative mood",
        ifelse(RelieveNegativeMood==4, "(4)Watch to mostly relieve negative mood",
        ifelse(RelieveNegativeMood==5, "(5)Watch to fully relieve negative mood", NA))))),
        DealWithAnxiety =
        ifelse(DealWithAnxiety==1, "(1)Does not watch ASMR videos to deal with anxiety",
        ifelse(DealWithAnxiety==2, "(2)Watch to minimally deal with anxiety",
        ifelse(DealWithAnxiety==3, "(3)Somewhat watches to deal with anxiety",
        ifelse(DealWithAnxiety==4, "(4)Mostly watches to deal with anxiety",
        ifelse(DealWithAnxiety==5, "(5)Fully watches to deal with anxiety", NA))))),
        DealWithStress =
        ifelse(DealWithStress==1, "(1)Does not watch ASMR videos to deal with stress",
        ifelse(DealWithStress==2, "(2)Watch to minimally deal with stress",
        ifelse(DealWithStress==3, "(3)Somewhat watches to deal with stress",
        ifelse(DealWithStress==4, "(4)Mostly watches to deal with stress",
        ifelse(DealWithStress==5, "(5)Fully watches to deal with stress", NA))))),
        WatchToDealWithDepression=
        ifelse(WatchToDealWithDepression==1, "(1)Does not watch ASMR videos to deal with depression",
        ifelse(WatchToDealWithDepression==2, "(2)Watch to minimally deal with depression",
        ifelse(WatchToDealWithDepression==3, "(3)Somewhat watches to deal with depression",
        ifelse(WatchToDealWithDepression==4, "(4)Mostly watches to deal with depression",
        ifelse(WatchToDealWithDepression==5, "(5)Fully watches to deal with depression", NA))))),
        HelpMeSleep =
        ifelse(HelpMeSleep==1, "(1)Does not watch ASMR videos to help with sleep",
        ifelse(HelpMeSleep==2, "(2)Watch to minimally help with sleep",
        ifelse(HelpMeSleep==3, "(3)Somewhat watches to help with sleep",
        ifelse(HelpMeSleep==4, "(4)Mostly watches to help with sleep",
        ifelse(HelpMeSleep==5, "(5)Fully watches to help with sleep", NA))))))%>%
  filter(!is.na(RelieveNegativeMood), !is.na(EnjoyASMRvideos), !is.na(WatchToRelax), !is.na(DealWithAnxiety),
         !is.na(DealWithStress), !is.na(WatchToDealWithDepression), !is.na(HelpMeSleep))
  
  
ggplot(asmr3, aes(x = BDI_group, y=BDI_TOTAL, fill = RelieveNegativeMood))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 20, vjust = 1),plot.title = element_text(hjust = 0.5), axis.title.x = element_text(vjust = 1))+
  labs(x = "BDI Group", title = "Relief of Negative Mood of Participants", y = "BDI Total Score")

ggplot(asmr3, aes(x = BDI_group, y=BDI_TOTAL, fill = DealWithAnxiety))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 20, vjust = 1),plot.title = element_text(hjust = 0.5), axis.title.x = element_text(vjust = 1))+
  labs(x = "BDI Group", title = "Watch to Deal With Anxiety", y = "BDI Total Score")

ggplot(asmr3, aes(x = BDI_group, y=BDI_TOTAL, fill = DealWithStress))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 20, vjust = 1),plot.title = element_text(hjust = 0.5), axis.title.x = element_text(vjust = 1))+
  labs(x = "BDI Group", title = "Watch to Deal with Stress", y = "BDI Total Score")

ggplot(asmr3, aes(x = BDI_group, y=BDI_TOTAL, fill = WatchToDealWithDepression))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 20, vjust = 1),plot.title = element_text(hjust = 0.5), axis.title.x = element_text(vjust = 1))+
  labs(x = "BDI Group", title = "Watch to Deal with Depression", y = "BDI Total Score")





```

# Facet-wrapped Bar graph

```{r}
ggplot(asmr3, aes(x = HelpMeSleep, fill = EffectSleep))+
  geom_bar(position="fill")+
  facet_wrap(~BDI_group)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5),plot.title = element_text(hjust = 0.5), axis.title.x = element_text(vjust = -1))+
  labs(x = "Watch ASMR videos to help sleep", title = "Sleep Effect on BDI groups")
```

# 3. Regression

# Multiple Linear Regression Model to predict Mood_After_watch

```{r}
# Building a model to predict the mood after watching
mood.data <- asmr_data3%>%
  select(BDI_TOTAL, Mood_Before_watch, Mood_During_Watch, Mood_After_watch, Mood_Daily)
bdimood.model <- lm(Mood_After_watch~., mood.data)
summary(bdimood.model)

```

# Using AIC to make a better multiple linear regression model

```{r}
# Using correlation matrix to see which predictor variables are better
mood.data%>%
  cor()

# Using AIC pick out the best predictors
library(MASS)
bdimood.model2 <- stepAIC(bdimood.model, direction = "both", trace = F)
detach("package:MASS")
summary(bdimood.model2)

```
# Predicting using the AIC Multilinear regression model

```{r}
# Creating values to predict in a data frame

newvalues <- data.frame(BDI_TOTAL = c(10,44,23), Mood_During_Watch = c(70,31,63), Mood_Daily = c(65,26,56))

predict(bdimood.model2, newvalues, interval = "predict")
```


# Logistic Regression Model to predict EffectSleep

```{r}

# First subsetting the data to only include the columns of the predictor variables and another one column for the binary response variable
effectsleep.data <- asmr_data3%>%
  mutate(EffectSleep2 = ifelse(EffectSleep == "Yes", 1, 0))%>%
  select(BDI_TOTAL, BAI_TOTAL, Mood_Daily, Mood_Before_watch, Mood_After_watch, Num_ASMRVideos, EffectSleep2)

# Building logistic regression model

logit <- glm(EffectSleep2~. , effectsleep.data, family = "binomial")


# Rebuilding logistic regression model to only include the most important variables by using AIC
library(MASS)
new.logit <- stepAIC(logit, direction = "both", trace = F)
summary(new.logit)
detach("package:MASS")

exp(coef(new.logit))
# Using new values to predict the outcome of EffectSleep

newvalues2 <- data.frame(BDI_TOTAL = c(15,25,47), BAI_TOTAL = c(6,22,33), Mood_Before_watch = c(85,55,21), Mood_After_watch = c(90,64,29))
predict(new.logit, newvalues2, type = "response")


```

# 4. Sample Inference

# Confidence Interval for Proportions (One Sample Inference)

```{r}
# First counting the data for how many participants said "Yes" to the EffectSleep variable
asmr_data3%>%
  filter(EffectSleep == "Yes")%>%
  summarize(EffectSleep_yes = n())


prop.test(282, 475, conf.level = 0.95)
```


# Confidence Interval for Means(TWo Sample Inference of Paired Populations)
```{r}
t.test(asmr_data3$Mood_Daily, asmr_data3$Mood_After_watch, paired = T, conf.level = 0.95)
```